\documentclass[letterpaper]{cv_brennen}

% This is just to get better error messages for debugging:
\setcounter{errorcontextlines}{100}

% For more compact lists.
\usepackage{paralist}
% Take up more of the page space.
\usepackage{fullpage}

\begin{document}

\author{Brennen Bearnes}
\phone{(402) 360-4362}
% Commented this out so to avoid Brennen Bearnes <bbearnes@gmail.com> in
% the header:
% \email{bbearnes@gmail.com}
% An actual webpage could go here, but I'm cheating so as not to muck
% with the class file:
\webpage{bbearnes@gmail.com}
\streetaddress{12191 Foothills Highway}
\citystatezip{Longmont, Colorado 80503}

\maketitle

\section{Education}

\affiliation{Wayne State College}{2000-2001}

\affiliation[Bachelor of Arts in History]
            {University of Nebraska}{2002-2004}

\begin{compactitem}
\item Authored survey and data collection software for political science
      research in decision making, elections, and measures of corruption.
      Contributed work to conference papers and a forthcoming journal article.
\item Conducted and transcribed interviews for Homestead National Monument's
      oral history project.
\item UNL Ultimate Frisbee Club
\item Selleck Hall Government, Husker Linux Users Group, Human Behavior and
      Evolution Reading Group
\end{compactitem}

\section{Experience}

\affiliation[Researcher, Photography Assistant]
            {Home \& Abroad, Inc.}{February 2006; May 2006-Present}

\begin{compactitem}
\item Extensive destination research for web-based custom travel guide.
\item Quality assurance, proofreading, and error correction.
\item Coordination, selection, and processing of photography for travel destinations.
\end{compactitem}

\affiliation[Account Associate]
            {Xerox / Sun Microsystems, Broomfield, CO}
            {September 2005-January 2006}

\begin{compactitem}
\item Received and coordinated delivery of shipments for seven-building campus.
      Frequent customer service.
\item Handled all phases of international and domestic shipping, from envelopes
      to multi-ton freight.
\item Monitored trouble-ticket system and distributed remote access hardware.
\end{compactitem}

\affiliation[Volunteer Teacher]
            {Tamariki School, Christchurch, New Zealand}{January-April 2005}

\begin{compactitem}
\item Worked with students (ages 5-13) and teachers to facilitate learning in a
      democratic environment.
\item Guided activities including sports, music, a mock post office and bank,
      basic computer skills, and art.
\item Participated in community discussions of democratic and alternative
      education; lived with students and families.
\end{compactitem}

\affiliation[Acquisitions Assistant, Native Studies]
            {University of Nebraska Press, Lincoln, NE}{Fall 2004}

\begin{compactitem}
\item Evaluated scholarly proposals and manuscripts, located external academic
      reviewers.
\item Communicated with authors through acquisition and preproduction process.
\item Researched and cleared text and image permissions.
\end{compactitem}

\affiliation{Bearnes Enterprises, Laurel, NE}{2001-2003}

\begin{compactitem}
\item Part Owner, retail sales of wood burning furnaces.
\item Assisted with sales, shows, and installations.
\end{compactitem}

\affiliation[Territory Sales Assistant]
            {Syngenta Seeds, Inc., Laurel, NE}{1997-2002 (seasonal)}

\begin{compactitem}
\item Seed delivery, assisted in planting and harvesting test plots, set up and
      planning of field days. 
\item Data collection and entry.
\end{compactitem}

\section{Technical Skills}

\noindent Skilled in Linux/FreeBSD administration, the Apache web server
platform, and XHTML/CSS. Experienced with Adobe Photoshop, the Gimp, \LaTeX,
and Perl/CGI. Familiar with most major end-user platforms, office software, etc.
Skilled in the use of wiki and wiki-like platforms (including MediaWiki,
usemod, and Confluence) for documentation and project coordination.

\end{document}
